### 2019-04-25 sections/intuition.tex

Collaboration in the real world consists of three aspects: communication, concurrency, and synchronisation.
These aspects are reflected in \TOP on a high level of abstraction, hiding the details of communication.
For example, the cigarette smokers communicate with each other, but the programs do not explicitly mention sending or receiving events.
By focussing on collaboration instead of communication, \TOP leads to specifications closer to real-world workflows which, at the same time, can be used to generate multi-user applications to support such workflows.

>>>>

Collaboration in the real world consists of three aspects: communication, concurrency, and synchronisation.
These aspects are reflected in \TOP on a high level of abstraction, hiding the details of communication.
For example, the cigarette smokers communicate with each other, but the programs do not explicitly mention sending or receiving events.

By focusing on collaboration instead of communication, \TOP leads to specifications closer to real-world workflows which, at the same time, can be used to generate multi-user applications to support such workflows.

### 2019-04-25 sections/properties.tex

In order to validate our semantics, we show that our evaluation, normalisation
and handling semantics is type preserving. We additionally prove a progress
theorem for our small-step handling semantics.
We show that our failing function $\Failing$ indeed only indicates expressions
that can not be normalised and that allow no further interaction.
Finally, we prove that the function to compute all possible inputs $\Inputs$ is sound and complete.

@@

Where $\Sigma \infers \sigma$ means that for all $l\in \sigma$, it holds that
$\Sigma(l)=\Gamma,\Sigma\infers \sigma(l)$.

>>>>

In order to show our semantics is sane, we show that our evaluation, normalisation
and handling semantics is type preserving. We additionally prove a progress
theorem for our small-step handling semantics.
We show that our failing function $\Failing$ indeed only indicates expressions
that can not be normalised and that allow no further interaction.
Finally, we prove that the function to compute all possible inputs $\Inputs$ is sound and complete.

@@

\noindent
Where $\Sigma \infers \sigma$ means that for all $l\in \sigma$, it holds that
$\Sigma(l)=\Gamma,\Sigma\infers \sigma(l)$.
